Flatiron cleaning

### 2021-09-22 Rmd/Report October 2021.Rmd
New report for meeting

---
title: "Flatiron analysis"
author: "Christelle Colin-Leitzinger"
date: '`r Sys.Date()`'
output: 
  html_document:
    toc: true
    toc_float: true
    toc_collapsed: false
    theme: flatly
    highlight: pygments
    df_print: paged
editor_options: 
  chunk_output_type: console
---

@@

# CALCULATE RDI

`r emo::ji("question_mark")`  
<span style="color:red">**I need confirmation : we calculate 1 RDI per drug per patient for the first (unique) line of neoadjuvant and 1 RDI per drug per patient for the ALL the lines of adjuvant which are not maintenance. Is that correct**</span>

## Calculate RDI by drug by cycle by patient
Here few examples
```{r, rows.print=15, max.print=30}
analysis_data <- analysis_data %>% 
  # Calculate RDI for each drug per cycle per patients
  mutate(relative_dose_intensity = amount/expected_dose) %>% 
  group_by(patientid, linenumber_new, cycle_drugname,  chemotherapy_type, linestartdate, lineenddate, cycle_increment) %>% 
  summarise(across(relative_dose_intensity, mean, na.rm = TRUE))

analysis_data
```

## Calculate RDI by drug by line by patient
Here few examples
```{r, rows.print=15, max.print=30}
analysis_data <- analysis_data %>% 
  # Calculate RDI for each drug per line per patients
  group_by(patientid, linenumber_new, cycle_drugname,  chemotherapy_type, linestartdate, lineenddate) %>% 
  summarise(across(relative_dose_intensity, mean, na.rm = TRUE))

analysis_data
```

## Calculate RDI by drug by patient
Here few examples
```{r, rows.print=15, max.print=30}
analysis_data <- analysis_data %>% 
  # Calculate RDI for each drug per patients
  group_by(patientid, cycle_drugname, chemotherapy_type) %>% 
  summarise(across(relative_dose_intensity, mean, na.rm = TRUE)) %>% 
  ungroup()

analysis_data

analysis_data %>% 
  ggplot(aes(x = relative_dose_intensity, fill = cycle_drugname))+
  geom_histogram(alpha = 0.5)+
  theme_minimal()+
  facet_wrap(.~ chemotherapy_type, scales = "free")

analysis_data %>% 
  ggplot(aes(x = relative_dose_intensity, y = chemotherapy_type, fill = cycle_drugname))+
  geom_boxplot()+
  geom_vline(xintercept = 1, color = "red")+
  theme_minimal()
```

```{r}
analysis_data <- analysis_data %>%

  mutate(RDI_grp = case_when(
    relative_dose_intensity < 0.85          ~ "RDI < 0.85",
    relative_dose_intensity >= 0.85         ~ "RDI >= 0.85"
  )) %>% 
  mutate(RDI_grp = factor(RDI_grp, 
                           labels = c("RDI >= 0.85", "RDI < 0.85"))) %>% 
  mutate(RDI_grp1 = case_when(
    relative_dose_intensity < 0.85          ~ "RDI < 0.85",
    # relative_dose_intensity >= 0.85         ~ "RDI >= 0.85",
    relative_dose_intensity >= 0.85 &
      relative_dose_intensity <= 1          ~ "0.85 <= RDI <= 1",
    relative_dose_intensity > 1 &
      relative_dose_intensity <= 1.5        ~ "1 < RDI <= 1.5",
    relative_dose_intensity > 1.5 &
      relative_dose_intensity <= 2          ~ "1.5 < RDI <= 2",
    relative_dose_intensity > 2             ~ "RDI > 2",
  )) %>% 
  mutate(RDI_grp1 = factor(RDI_grp1, 
                          labels = c("RDI < 0.85", 
                                     "0.85 >= RDI <= 1", 
                                     "1 < RDI <= 1.5", 
                                     "1.5 < RDI <= 2", 
                                     "RDI > 2"))) %>% 
  # mutate(delay_incare_dx_to_treat = case_when(
  #   str_detect(therapy, "Chemo")     ~ (interval(start = diagnosisdate, end = episodedate)/
  #     duration(n=1, units = "days")),
  #   str_detect(therapy, "Surgery")   ~ (interval(start = diagnosisdate, end = surgerydate)/
  #     duration(n=1, units = "days"))
  # )) %>% 
  left_join(., Treatment) %>% 
  group_by(patientid) %>%
  mutate(first_treatment_date = case_when(
    treatment_sequence == "Chemotherapy only"             ~ min(episodedate),
    str_detect(treatment_sequence, "neo")                 ~ min(episodedate),
    treatment_sequence == "surg + adj"                    ~ surgerydate,
    treatment_sequence == "Surgery only"                  ~ surgerydate
  )) %>%
  # group_by(patientid) %>% 
  # mutate(first_treatment_date = case_when(
  #   str_detect(therapy, "Chemo")                      ~ min(episodedate),
  #   str_detect(therapy, "Surgery")                    ~ surgerydate,
  # )) %>% 
  # mutate(delay_incare_dx_to_treat = interval(start = diagnosisdate, end = first_treatment_date)/
  #                                         duration(n=1, units = "days")) %>% 
  mutate(month_at_os_from_treatment = interval(start = first_treatment_date, end = followupdate)/
                   duration(n=1, units = "months")) %>% 
  ungroup()

```

@@

## 2.Plots Clinical
<div class = "row">
<div class = "col-md-6">
```{r}
analysis_data %>% 
  distinct(patientid, .keep_all = TRUE) %>% 
  ggplot(aes(x= bmi_cat))+
  geom_bar()+
  theme_minimal()+
  labs(title = "BMI category")+
  coord_flip()

analysis_data %>% 
  distinct(patientid, .keep_all = TRUE) %>% 
  ggplot(aes(x= histology))+
  geom_bar()+
  theme_minimal()+
  labs(title = "Histology")+
  coord_flip()

analysis_data %>% 
  distinct(patientid, .keep_all = TRUE) %>% 
  ggplot(aes(x= stagecat))+
  geom_bar()+
  theme_minimal()+
  labs(title = "Stage")+
  coord_flip()

analysis_data %>% 
  distinct(patientid, .keep_all = TRUE) %>% 
  ggplot(aes(x= agecat))+
  geom_bar()+
  theme_minimal()+
  labs(title = "Age cat")+
  coord_flip()

analysis_data %>% 
  distinct(patientid, .keep_all = TRUE) %>% 
  ggplot(aes(x= brca_germline))+
  geom_bar()+
  theme_minimal()+
  labs(title = "BRCA gernline")+
  coord_flip()

analysis_data %>% 
  distinct(patientid, .keep_all = TRUE) %>% 
  ggplot(aes(x= brca_tumor))+
  geom_bar()+
  theme_minimal()+
  labs(title = "BRCA tumor")+
  coord_flip()
```
</div>

<div class = "col-md-6">
```{r}
analysis_data %>% 
  distinct(patientid, .keep_all = TRUE) %>% 
  ggplot(aes(x= raceeth, fill = bmi_cat))+
  geom_bar(position = "fill")+
  theme_minimal()+
  labs(title = "BMI category")+
  coord_flip()

analysis_data %>% 
  distinct(patientid, .keep_all = TRUE) %>% 
  ggplot(aes(x= histology, fill = raceeth))+
  geom_bar(position = "fill")+
  theme_minimal()+
  labs(title = "Histology")+
  coord_flip()

analysis_data %>% 
  distinct(patientid, .keep_all = TRUE) %>% 
  ggplot(aes(x= stagecat, fill = raceeth))+
  geom_bar(position = "fill")+
  theme_minimal()+
  labs(title = "Stage")+
  coord_flip()

analysis_data %>% 
  distinct(patientid, .keep_all = TRUE) %>% 
  ggplot(aes(x= agecat, fill = raceeth))+
  geom_bar(position = "fill")+
  theme_minimal()+
  labs(title = "Age cat")+
  coord_flip()

analysis_data %>% 
  distinct(patientid, .keep_all = TRUE) %>% 
  ggplot(aes(x= brca_germline, fill = raceeth))+
  geom_bar(position = "fill")+
  theme_minimal()+
  labs(title = "BRCA germline")+
  coord_flip()

analysis_data %>% 
  distinct(patientid, .keep_all = TRUE) %>% 
  ggplot(aes(x= brca_tumor, fill = raceeth))+
  geom_bar(position = "fill")+
  theme_minimal()+
  labs(title = "BRCA tumor")+
  coord_flip()
```
</div>
</div>

## 3.Survivals by clinical

<span style="color:green">**Survival plots from date of diagnosis on the left and from date of treatment on the right**</span>

<div class = "row">
<div class = "col-md-6">
```{r clinical from dx, fig.height = 7}
# OS by race
# ggsurvplot(survfit(Surv(month_at_os, vitalstatus) ~ race, data=analysis_data),
#            title = "OS from date of diagnosis", 
#            font.main = c(24, "bold", "black"), 
#            font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"), 
#            font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"), 
#            size = 1.5,
#            
#            pval=TRUE, 
#            # legend.labs=c(""),
#            # palette = c("black", "green","blue", "red"), 
#            # Add risk table
#            risk.table = "abs_pct", risk.table.title = "Risk table (number(%))",
#            risk.table.y.text = FALSE, risk.table.fontsize = 3, tables.height = 0.3,
#            tables.theme = theme_survminer(base_size = 5,
#                                           font.main = c(16, "bold", "black"),
#                                           font.x = c(16, "bold", "black"),
#                                           font.y = c(16, "bold", "transparent"),
#                                           font.tickslab = c(19, "bold", "black")
#            ),
#            
#            legend.title = "", xlab = "Time (in months)" 
# ) + guides(colour = guide_legend(ncol = 2))

# OS by raceeth
ggsurvplot(survfit(Surv(month_at_os, vitalstatus) ~ raceeth, data=analysis_data %>% 
                     distinct(patientid, .keep_all = TRUE)),
           title = "OS from date of diagnosis", 
           font.main = c(24, "bold", "black"), 
           font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"), 
           font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"), 
           size = 1.5,

           pval=TRUE, 
           # legend.labs=c(""),
           # palette = c("black", "green","blue", "red"), 
           # Add risk table
           risk.table = "abs_pct", risk.table.title = "Risk table (number(%))",
           risk.table.y.text = FALSE, risk.table.fontsize = 3, tables.height = 0.3,
           tables.theme = theme_survminer(base_size = 5,
                                          font.main = c(16, "bold", "black"),
                                          font.x = c(16, "bold", "black"),
                                          font.y = c(16, "bold", "transparent"),
                                          font.tickslab = c(19, "bold", "black")
           ),

           legend.title = "", xlab = "Time (in months)" 
) + guides(colour = guide_legend(ncol = 2))

# OS by histology
# ggsurvplot(survfit(Surv(month_at_os, vitalstatus) ~ histology, data=analysis_data %>% 
#                      distinct(patientid, .keep_all = TRUE)),
#            title = "OS from date of diagnosis", 
#            font.main = c(24, "bold", "black"), 
#            font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"), 
#            font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"), 
#            size = 1.5,
#            
#            pval=TRUE, 
#            # legend.labs=c(""),
#            # palette = c("black", "green","blue", "red"), 
#            # Add risk table
#            risk.table = "abs_pct", risk.table.title = "Risk table (number(%))",
#            risk.table.y.text = FALSE, risk.table.fontsize = 3, tables.height = 0.3,
#            tables.theme = theme_survminer(base_size = 5,
#                                           font.main = c(16, "bold", "black"),
#                                           font.x = c(16, "bold", "black"),
#                                           font.y = c(16, "bold", "transparent"),
#                                           font.tickslab = c(19, "bold", "black")
#            ),
#            
#            legend.title = "", xlab = "Time (in months)" 
# ) + guides(colour = guide_legend(ncol = 2))

# OS by tstage
ggsurvplot(survfit(Surv(month_at_os, vitalstatus) ~ stagecat, data=analysis_data %>% 
                     distinct(patientid, .keep_all = TRUE)),
           title = "OS from date of diagnosis", 
           font.main = c(24, "bold", "black"), 
           font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"), 
           font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"), 
           size = 1.5,

           pval=TRUE, 
           # legend.labs=c(""),
           # palette = c("black", "green","blue", "red"), 
           # Add risk table
           risk.table = "abs_pct", risk.table.title = "Risk table (number(%))",
           risk.table.y.text = FALSE, risk.table.fontsize = 3, tables.height = 0.3,
           tables.theme = theme_survminer(base_size = 5,
                                          font.main = c(16, "bold", "black"),
                                          font.x = c(16, "bold", "black"),
                                          font.y = c(16, "bold", "transparent"),
                                          font.tickslab = c(19, "bold", "black")
           ),

           legend.title = "", xlab = "Time (in months)" 
) + guides(colour = guide_legend(ncol = 2))

# OS by bmi_cat
ggsurvplot(survfit(Surv(month_at_os, vitalstatus) ~ bmi_cat, data=analysis_data %>% 
                     distinct(patientid, .keep_all = TRUE)),
           title = "OS from date of diagnosis", 
           font.main = c(24, "bold", "black"), 
           font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"), 
           font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"), 
           size = 1.5,

           pval=TRUE, 
           # legend.labs=c(""),
           # palette = c("black", "green","blue", "red"), 
           # Add risk table
           risk.table = "abs_pct", risk.table.title = "Risk table (number(%))",
           risk.table.y.text = FALSE, risk.table.fontsize = 3, tables.height = 0.3,
           tables.theme = theme_survminer(base_size = 5,
                                          font.main = c(16, "bold", "black"),
                                          font.x = c(16, "bold", "black"),
                                          font.y = c(16, "bold", "transparent"),
                                          font.tickslab = c(19, "bold", "black")
           ),

           legend.title = "", xlab = "Time (in months)" 
) + guides(colour = guide_legend(ncol = 2))

# OS by brca1_tumor
ggsurvplot(survfit(Surv(month_at_os, vitalstatus) ~ brca1_tumor, data=analysis_data %>% 
                     distinct(patientid, .keep_all = TRUE)),
           title = "OS from date of diagnosis", 
           font.main = c(24, "bold", "black"), 
           font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"), 
           font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"), 
           size = 1.5,

           pval=TRUE, 
           # legend.labs=c(""),
           # palette = c("black", "green","blue", "red"), 
           # Add risk table
           risk.table = "abs_pct", risk.table.title = "Risk table (number(%))",
           risk.table.y.text = FALSE, risk.table.fontsize = 3, tables.height = 0.3,
           tables.theme = theme_survminer(base_size = 5,
                                          font.main = c(16, "bold", "black"),
                                          font.x = c(16, "bold", "black"),
                                          font.y = c(16, "bold", "transparent"),
                                          font.tickslab = c(19, "bold", "black")
           ),

           legend.title = "", xlab = "Time (in months)" 
) + guides(colour = guide_legend(ncol = 2))

# OS by brca2_tumor
ggsurvplot(survfit(Surv(month_at_os, vitalstatus) ~ brca2_tumor, data=analysis_data %>% 
                     distinct(patientid, .keep_all = TRUE)),
           title = "OS from date of diagnosis", 
           font.main = c(24, "bold", "black"), 
           font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"), 
           font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"), 
           size = 1.5,

           pval=TRUE, 
           # legend.labs=c(""),
           # palette = c("black", "green","blue", "red"), 
           # Add risk table
           risk.table = "abs_pct", risk.table.title = "Risk table (number(%))",
           risk.table.y.text = FALSE, risk.table.fontsize = 3, tables.height = 0.3,
           tables.theme = theme_survminer(base_size = 5,
                                          font.main = c(16, "bold", "black"),
                                          font.x = c(16, "bold", "black"),
                                          font.y = c(16, "bold", "transparent"),
                                          font.tickslab = c(19, "bold", "black")
           ),

           legend.title = "", xlab = "Time (in months)" 
) + guides(colour = guide_legend(ncol = 2))

# OS by brca_tumor
ggsurvplot(survfit(Surv(month_at_os, vitalstatus) ~ brca_tumor, data=analysis_data %>% 
                     distinct(patientid, .keep_all = TRUE)),
           title = "OS from date of diagnosis", 
           font.main = c(24, "bold", "black"), 
           font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"), 
           font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"), 
           size = 1.5,

           pval=TRUE, 
           # legend.labs=c(""),
           # palette = c("black", "green","blue", "red"), 
           # Add risk table
           risk.table = "abs_pct", risk.table.title = "Risk table (number(%))",
           risk.table.y.text = FALSE, risk.table.fontsize = 3, tables.height = 0.3,
           tables.theme = theme_survminer(base_size = 5,
                                          font.main = c(16, "bold", "black"),
                                          font.x = c(16, "bold", "black"),
                                          font.y = c(16, "bold", "transparent"),
                                          font.tickslab = c(19, "bold", "black")
           ),

           legend.title = "", xlab = "Time (in months)" 
) + guides(colour = guide_legend(ncol = 2))

# OS by brca1_g
ggsurvplot(survfit(Surv(month_at_os, vitalstatus) ~ brca1_germline, data=analysis_data %>% 
                     distinct(patientid, .keep_all = TRUE)),
           title = "OS from date of diagnosis", 
           font.main = c(24, "bold", "black"), 
           font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"), 
           font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"), 
           size = 1.5,

           pval=TRUE, 
           # legend.labs=c(""),
           # palette = c("black", "green","blue", "red"), 
           # Add risk table
           risk.table = "abs_pct", risk.table.title = "Risk table (number(%))",
           risk.table.y.text = FALSE, risk.table.fontsize = 3, tables.height = 0.3,
           tables.theme = theme_survminer(base_size = 5,
                                          font.main = c(16, "bold", "black"),
                                          font.x = c(16, "bold", "black"),
                                          font.y = c(16, "bold", "transparent"),
                                          font.tickslab = c(19, "bold", "black")
           ),

           legend.title = "", xlab = "Time (in months)" 
) + guides(colour = guide_legend(ncol = 2))

# OS by brca2_g
ggsurvplot(survfit(Surv(month_at_os, vitalstatus) ~ brca2_germline, data=analysis_data %>% 
                     distinct(patientid, .keep_all = TRUE)),
           title = "OS from date of diagnosis", 
           font.main = c(24, "bold", "black"), 
           font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"), 
           font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"), 
           size = 1.5,

           pval=TRUE, 
           # legend.labs=c(""),
           # palette = c("black", "green","blue", "red"), 
           # Add risk table
           risk.table = "abs_pct", risk.table.title = "Risk table (number(%))",
           risk.table.y.text = FALSE, risk.table.fontsize = 3, tables.height = 0.3,
           tables.theme = theme_survminer(base_size = 5,
                                          font.main = c(16, "bold", "black"),
                                          font.x = c(16, "bold", "black"),
                                          font.y = c(16, "bold", "transparent"),
                                          font.tickslab = c(19, "bold", "black")
           ),

           legend.title = "", xlab = "Time (in months)" 
) + guides(colour = guide_legend(ncol = 2))

# OS by brca_g
ggsurvplot(survfit(Surv(month_at_os, vitalstatus) ~ brca_germline, data=analysis_data %>% 
                     distinct(patientid, .keep_all = TRUE)),
           title = "OS from date of diagnosis", 
           font.main = c(24, "bold", "black"), 
           font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"), 
           font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"), 
           size = 1.5,

           pval=TRUE, 
           # legend.labs=c(""),
           # palette = c("black", "green","blue", "red"), 
           # Add risk table
           risk.table = "abs_pct", risk.table.title = "Risk table (number(%))",
           risk.table.y.text = FALSE, risk.table.fontsize = 3, tables.height = 0.3,
           tables.theme = theme_survminer(base_size = 5,
                                          font.main = c(16, "bold", "black"),
                                          font.x = c(16, "bold", "black"),
                                          font.y = c(16, "bold", "transparent"),
                                          font.tickslab = c(19, "bold", "black")
           ),

           legend.title = "", xlab = "Time (in months)" 
) + guides(colour = guide_legend(ncol = 2))
```
</div>

<div class = "col-md-6">
```{r clinical from first treatment, fig.height = 7}
# OS by race
# ggsurvplot(survfit(Surv(month_at_os_from_treatment, vitalstatus) ~ race, data=analysis_data %>% 
#                      distinct(patientid, .keep_all = TRUE)),
#            title = "OS from date of first treatment", 
#            font.main = c(24, "bold", "black"), 
#            font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"), 
#            font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"), 
#            size = 1.5,
#            
#            pval=TRUE, 
#            # legend.labs=c(""),
#            # palette = c("black", "green","blue", "red"), 
#            # Add risk table
#            risk.table = "abs_pct", risk.table.title = "Risk table (number(%))",
#            risk.table.y.text = FALSE, risk.table.fontsize = 3, tables.height = 0.3,
#            tables.theme = theme_survminer(base_size = 5,
#                                           font.main = c(16, "bold", "black"),
#                                           font.x = c(16, "bold", "black"),
#                                           font.y = c(16, "bold", "transparent"),
#                                           font.tickslab = c(19, "bold", "black")
#            ),
#            
#            legend.title = "", xlab = "Time (in months)" 
# ) + guides(colour = guide_legend(ncol = 2))

# OS by raceeth
ggsurvplot(survfit(Surv(month_at_os_from_treatment, vitalstatus) ~ raceeth, data=analysis_data %>% 
                     distinct(patientid, .keep_all = TRUE)),
           title = "OS from date of first treatment", 
           font.main = c(24, "bold", "black"), 
           font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"), 
           font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"), 
           size = 1.5,

           pval=TRUE, 
           # legend.labs=c(""),
           # palette = c("black", "green","blue", "red"), 
           # Add risk table
           risk.table = "abs_pct", risk.table.title = "Risk table (number(%))",
           risk.table.y.text = FALSE, risk.table.fontsize = 3, tables.height = 0.3,
           tables.theme = theme_survminer(base_size = 5,
                                          font.main = c(16, "bold", "black"),
                                          font.x = c(16, "bold", "black"),
                                          font.y = c(16, "bold", "transparent"),
                                          font.tickslab = c(19, "bold", "black")
           ),

           legend.title = "", xlab = "Time (in months)" 
) + guides(colour = guide_legend(ncol = 2))

# OS by histology
# ggsurvplot(survfit(Surv(month_at_os_from_treatment, vitalstatus) ~ histology, data=analysis_data %>% 
#                      distinct(patientid, .keep_all = TRUE)),
#            title = "OS from date of first treatment", 
#            font.main = c(24, "bold", "black"), 
#            font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"), 
#            font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"), 
#            size = 1.5,
#            
#            pval=TRUE, 
#            # legend.labs=c(""),
#            # palette = c("black", "green","blue", "red"), 
#            # Add risk table
#            risk.table = "abs_pct", risk.table.title = "Risk table (number(%))",
#            risk.table.y.text = FALSE, risk.table.fontsize = 3, tables.height = 0.3,
#            tables.theme = theme_survminer(base_size = 5,
#                                           font.main = c(16, "bold", "black"),
#                                           font.x = c(16, "bold", "black"),
#                                           font.y = c(16, "bold", "transparent"),
#                                           font.tickslab = c(19, "bold", "black")
#            ),
#            
#            legend.title = "", xlab = "Time (in months)" 
# ) + guides(colour = guide_legend(ncol = 2))

# OS by tstage
ggsurvplot(survfit(Surv(month_at_os_from_treatment, vitalstatus) ~ stagecat, data=analysis_data %>% 
                     distinct(patientid, .keep_all = TRUE)),
           title = "OS from date of first treatment", 
           font.main = c(24, "bold", "black"), 
           font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"), 
           font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"), 
           size = 1.5,

           pval=TRUE, 
           # legend.labs=c(""),
           # palette = c("black", "green","blue", "red"), 
           # Add risk table
           risk.table = "abs_pct", risk.table.title = "Risk table (number(%))",
           risk.table.y.text = FALSE, risk.table.fontsize = 3, tables.height = 0.3,
           tables.theme = theme_survminer(base_size = 5,
                                          font.main = c(16, "bold", "black"),
                                          font.x = c(16, "bold", "black"),
                                          font.y = c(16, "bold", "transparent"),
                                          font.tickslab = c(19, "bold", "black")
           ),

           legend.title = "", xlab = "Time (in months)" 
) + guides(colour = guide_legend(ncol = 2))

# OS by bmi_cat
ggsurvplot(survfit(Surv(month_at_os_from_treatment, vitalstatus) ~ bmi_cat, data=analysis_data %>% 
                     distinct(patientid, .keep_all = TRUE)),
           title = "OS from date of first treatment", 
           font.main = c(24, "bold", "black"), 
           font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"), 
           font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"), 
           size = 1.5,

           pval=TRUE, 
           # legend.labs=c(""),
           # palette = c("black", "green","blue", "red"), 
           # Add risk table
           risk.table = "abs_pct", risk.table.title = "Risk table (number(%))",
           risk.table.y.text = FALSE, risk.table.fontsize = 3, tables.height = 0.3,
           tables.theme = theme_survminer(base_size = 5,
                                          font.main = c(16, "bold", "black"),
                                          font.x = c(16, "bold", "black"),
                                          font.y = c(16, "bold", "transparent"),
                                          font.tickslab = c(19, "bold", "black")
           ),

           legend.title = "", xlab = "Time (in months)" 
) + guides(colour = guide_legend(ncol = 2))

# OS by brca1_tumor
ggsurvplot(survfit(Surv(month_at_os_from_treatment, vitalstatus) ~ brca1_tumor, data=analysis_data %>% 
                     distinct(patientid, .keep_all = TRUE)),
           title = "OS from date of first treatment", 
           font.main = c(24, "bold", "black"), 
           font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"), 
           font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"), 
           size = 1.5,

           pval=TRUE, 
           # legend.labs=c(""),
           # palette = c("black", "green","blue", "red"), 
           # Add risk table
           risk.table = "abs_pct", risk.table.title = "Risk table (number(%))",
           risk.table.y.text = FALSE, risk.table.fontsize = 3, tables.height = 0.3,
           tables.theme = theme_survminer(base_size = 5,
                                          font.main = c(16, "bold", "black"),
                                          font.x = c(16, "bold", "black"),
                                          font.y = c(16, "bold", "transparent"),
                                          font.tickslab = c(19, "bold", "black")
           ),

           legend.title = "", xlab = "Time (in months)" 
) + guides(colour = guide_legend(ncol = 2))

# OS by brca2_tumor
ggsurvplot(survfit(Surv(month_at_os_from_treatment, vitalstatus) ~ brca2_tumor, data=analysis_data %>% 
                     distinct(patientid, .keep_all = TRUE)),
           title = "OS from date of first treatment", 
           font.main = c(24, "bold", "black"), 
           font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"), 
           font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"), 
           size = 1.5,

           pval=TRUE, 
           # legend.labs=c(""),
           # palette = c("black", "green","blue", "red"), 
           # Add risk table
           risk.table = "abs_pct", risk.table.title = "Risk table (number(%))",
           risk.table.y.text = FALSE, risk.table.fontsize = 3, tables.height = 0.3,
           tables.theme = theme_survminer(base_size = 5,
                                          font.main = c(16, "bold", "black"),
                                          font.x = c(16, "bold", "black"),
                                          font.y = c(16, "bold", "transparent"),
                                          font.tickslab = c(19, "bold", "black")
           ),

           legend.title = "", xlab = "Time (in months)" 
) + guides(colour = guide_legend(ncol = 2))

# OS by brca_tumor
ggsurvplot(survfit(Surv(month_at_os_from_treatment, vitalstatus) ~ brca_tumor, data=analysis_data %>% 
                     distinct(patientid, .keep_all = TRUE)),
           title = "OS from date of first treatment", 
           font.main = c(24, "bold", "black"), 
           font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"), 
           font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"), 
           size = 1.5,

           pval=TRUE, 
           # legend.labs=c(""),
           # palette = c("black", "green","blue", "red"), 
           # Add risk table
           risk.table = "abs_pct", risk.table.title = "Risk table (number(%))",
           risk.table.y.text = FALSE, risk.table.fontsize = 3, tables.height = 0.3,
           tables.theme = theme_survminer(base_size = 5,
                                          font.main = c(16, "bold", "black"),
                                          font.x = c(16, "bold", "black"),
                                          font.y = c(16, "bold", "transparent"),
                                          font.tickslab = c(19, "bold", "black")
           ),

           legend.title = "", xlab = "Time (in months)" 
) + guides(colour = guide_legend(ncol = 2))
# OS by brca1_g
ggsurvplot(survfit(Surv(month_at_os_from_treatment, vitalstatus) ~ brca1_germline, data=analysis_data %>% 
                     distinct(patientid, .keep_all = TRUE)),
           title = "OS from date of first treatment", 
           font.main = c(24, "bold", "black"), 
           font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"), 
           font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"), 
           size = 1.5,

           pval=TRUE, 
           # legend.labs=c(""),
           # palette = c("black", "green","blue", "red"), 
           # Add risk table
           risk.table = "abs_pct", risk.table.title = "Risk table (number(%))",
           risk.table.y.text = FALSE, risk.table.fontsize = 3, tables.height = 0.3,
           tables.theme = theme_survminer(base_size = 5,
                                          font.main = c(16, "bold", "black"),
                                          font.x = c(16, "bold", "black"),
                                          font.y = c(16, "bold", "transparent"),
                                          font.tickslab = c(19, "bold", "black")
           ),

           legend.title = "", xlab = "Time (in months)" 
) + guides(colour = guide_legend(ncol = 2))

# OS by brca2_g
ggsurvplot(survfit(Surv(month_at_os_from_treatment, vitalstatus) ~ brca2_germline, data=analysis_data %>% 
                     distinct(patientid, .keep_all = TRUE)),
           title = "OS from date of first treatment", 
           font.main = c(24, "bold", "black"), 
           font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"), 
           font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"), 
           size = 1.5,

           pval=TRUE, 
           # legend.labs=c(""),
           # palette = c("black", "green","blue", "red"), 
           # Add risk table
           risk.table = "abs_pct", risk.table.title = "Risk table (number(%))",
           risk.table.y.text = FALSE, risk.table.fontsize = 3, tables.height = 0.3,
           tables.theme = theme_survminer(base_size = 5,
                                          font.main = c(16, "bold", "black"),
                                          font.x = c(16, "bold", "black"),
                                          font.y = c(16, "bold", "transparent"),
                                          font.tickslab = c(19, "bold", "black")
           ),

           legend.title = "", xlab = "Time (in months)" 
) + guides(colour = guide_legend(ncol = 2))

# OS by brca_g
ggsurvplot(survfit(Surv(month_at_os_from_treatment, vitalstatus) ~ brca_germline, data=analysis_data %>% 
                     distinct(patientid, .keep_all = TRUE)),
           title = "OS from date of first treatment", 
           font.main = c(24, "bold", "black"), 
           font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"), 
           font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"), 
           size = 1.5,

           pval=TRUE, 
           # legend.labs=c(""),
           # palette = c("black", "green","blue", "red"), 
           # Add risk table
           risk.table = "abs_pct", risk.table.title = "Risk table (number(%))",
           risk.table.y.text = FALSE, risk.table.fontsize = 3, tables.height = 0.3,
           tables.theme = theme_survminer(base_size = 5,
                                          font.main = c(16, "bold", "black"),
                                          font.x = c(16, "bold", "black"),
                                          font.y = c(16, "bold", "transparent"),
                                          font.tickslab = c(19, "bold", "black")
           ),

           legend.title = "", xlab = "Time (in months)" 
) + guides(colour = guide_legend(ncol = 2))
```
</div>
</div>

<br>
<br>

@@

## 3.Survivals by treatment

<div class = "row">
<div class = "col-md-6">
```{r, fig.height = 7}
ggsurvplot(survfit(Surv(month_at_os, vitalstatus) ~ issurgery, data=analysis_data %>% 
                     distinct(patientid, .keep_all = TRUE)),
           title = "OS from date of diagnosis", 
           font.main = c(24, "bold", "black"), 
           font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"), 
           font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"), 
           size = 1.5,

           pval=TRUE, 
           # legend.labs=c(""),
           # palette = c("black", "green","blue", "red"), 
           # Add risk table
           risk.table = "abs_pct", risk.table.title = "Risk table (number(%))",
           risk.table.y.text = FALSE, risk.table.fontsize = 3, tables.height = 0.3,
           tables.theme = theme_survminer(base_size = 5,
                                          font.main = c(16, "bold", "black"),
                                          font.x = c(16, "bold", "black"),
                                          font.y = c(16, "bold", "transparent"),
                                          font.tickslab = c(19, "bold", "black")
           ),

>>>>

---
title: "Flatiron cleaning"
author: "Christelle Colin-Leitzinger"
date: '`r Sys.Date()`'
output: 
  html_document:
    toc: true
    toc_float: true
    toc_collapsed: false
    theme: flatly
    highlight: pygments
    df_print: paged
editor_options: 
  chunk_output_type: console
---

@@

@@

@@

`expected_dose` is:  
-`target_auc` * (`CrCl` + 25)   -> for `drugname` == "carboplatin"  
-`BSA` * `target_auc`           -> for `drugname` == "taxel" or "cisplatin"  
(Again keep in mind that `target_auc` is just the name of the column in the data but is calculated differently depending of the drug name)  
It was capped to 900 when was > 900 for a `target_auc` of 6 and to 750 when was > 750 for a `target_auc` of 5 (Carboplatin).
